An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 indicators/paper/paper.tex
Add nearly all middle authors

% Middle authors
\author[d]{Middle Authors to be Added}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
\affil[d]{Remaining affiliations to be added}

>>>>

% Middle authors
\author[i]{Sumit Agrawal}
\author[l]{Wael Al Saeed}
\author[g]{Taylor Arnold}
\author[j]{Amartya Basu}
\author[d]{Jacob Bien}
\author[r]{Ángel Alexander Cabrera}
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[i]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[i]{David C. Farrow}
\author[r]{Jodi Forlizzi}
\author[i]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[r]{Robin Han}
\author[i]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[i]{Raphael Hyde}
\author[d]{Sangwon Hyun}
\author[l]{Ananya Joshi}
\author[h]{Jimi Kim}
\author[r]{Andrew Kuznetsov}
\author[b]{Wichada La~Motte-Kerr}
\author[f]{Balasubramanian Narasimhan}
\author[r]{Jenny Yeon Jin Lee}
\author[p]{Kenneth Lee}
\author[b]{Zachary C. Lipton}
\author[r]{Michael Xieyang Liu}
\author[k]{Lester Mackey}
\author[b]{Kathryn Mazaitis}
\author[o]{Daniel J. McDonald}
\author[i]{Phillip McGuinness}
\author[i]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[r]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[l]{Dawn Rucker}
\author[i]{Chris Scott}
\author[s]{Nigam Shah}
\author[n]{Vishnu Shankar}
\author[p]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[q]{Noah Simon}
\author[i]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[e,f]{Robert Tibshirani}
\author[e]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Valérie Ventura}
\author[a]{Larry Wasserman}
\author[i]{Benjamin Weaver}
\author[m]{Jeremy C. Weiss}
\author[i]{Spencer Whitman}
\author[r]{Kristin Williams}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
\affil[d]{Department of Data Sciences and Operations, University of Southern California}
\affil[e]{Department of Statistics, Stanford University}
\affil[f]{Department of Biomedical Data Science, Stanford University}
\affil[g]{Linguistics Program, University of Richmond}
\affil[h]{School of Natural Sciences and Mathematics, University of Texas at Dallas}
\affil[i]{Google.org}
\affil[j]{Information Networking Institute, Carnegie Mellon University}
\affil[k]{Microsoft Research New England}
\affil[l]{Computer Science Department, Carnegie Mellon University}
\affil[m]{Heinz College of Information Systems and Public Policy, Carnegie
  Mellon University}
\affil[n]{Program in Immunology, Stanford University School of Medicine}
\affil[o]{Department of Statistics, University of British Columbia}
\affil[p]{Department of Statistics, University of California, Davis}
\affil[q]{Department of Biostatistics, University of Washington}
\affil[r]{Human-Computer Interaction Institute, Carnegie Mellon University}
\affil[s]{Department of Medicine, Stanford University}
